---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# juicydown

<!-- badges: start -->
[![R-CMD-check](https://github.com/kenjisato/juicydown/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kenjisato/juicydown/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of juicydown is to offer useful tools to minimize routine formatting of 
page contents on such CMS as Moodle where code editor silently ignore style and 
link tags. To generate CSS-inlined HTML, the package uses [juicyjuce] package 
along with [knitr] and [markdown] packages. 

## Installation

You can install the development version of juicydown from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("kenjisato/juicydown")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(juicydown)
## basic example code
```

